---
title: "Repeating codes"
author: "Arun Prakash Krishnasamy"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
library(sf)
library(dplyr)
library(ggplot2)
```

```{r Geopackage - Task 4, message = FALSE}
gpkg_layers <- st_layers("data/Geopackage_2021_G02_VIC_GDA2020/G02_VIC_GDA2020.gpkg")
gpkg_layers

```

```{r SA1 data from GPKG - Task 4}

vicmap_sa1_G02 <- read_sf("data/Geopackage_2021_G02_VIC_GDA2020/G02_VIC_GDA2020.gpkg", layer = "G02_SA1_2021_VIC")
vicmap_sa1_G02
names(vicmap_sa1_G02)

```

```{r Wrangling data for Map MWR - Task 4}
# Set projection to GDA1994 using EPSG:4283
st_crs(aec_map$geometry,4283)
  
# Transform projection from GDA1994 to GDA2020 using EPSG:7844
aec_map$geometry = st_transform(aec_map$geometry, 7844) 

# Get SA1 Centroids
vicmap_sa1_G02_w_centroid <- vicmap_sa1_G02 |>
  mutate(centroid = st_centroid(geom))

# Determine with SA1 centroids overlap with which electoral regions
electoral_intersects = st_intersects(vicmap_sa1_G02_w_centroid$centroid, 
                               aec_map$geometry, 
                               sparse = FALSE) 
arr_ind = which(electoral_intersects == TRUE, arr.ind = TRUE)
sa1_ind = arr_ind[,1] 
division_ind = arr_ind[,2]
division_name = aec_map$Elect_div[division_ind]
sa1_name = vicmap_sa1_G02_w_centroid$SA1_NAME_2021[sa1_ind]

# Save the SA1 region and its matching electorate into a data frame
sa1_divisions = data.frame(SA1_NAME_2021 = sa1_name, 
                           DivisionNm = division_name)

# Add the electorate names to the map
vicmap_sa1_G02_electorates  <- vicmap_sa1_G02 %>% 
  right_join(sa1_divisions)

# Combine the data from electorates together using group_by
vicmap_sa1_G02_electorates_grouped_MWR =  vicmap_sa1_G02_electorates |>
  group_by(DivisionNm) |> 
  summarise(Median_rent_weekly = mean(Median_rent_weekly)) |>
  ungroup()

# Plot results to check assignment

VIC_map_MWR <- ggplot() +
   geom_sf(data = vicmap_sa1_G02_electorates_grouped_MWR,
           aes(geometry = geom, fill = Median_rent_weekly)) + 
  theme_bw() +
  theme(legend.position = "bottom")
VIC_map_MWR

```


Map of the entire state of Victoria, with its median weekly rent, is not a good visualization to draw conclusions from, as a result a scoped view would give us more clear picture.

For this we choose certain electorates and set the coordinate limits of the maps
```{r Scoped view of Map MWR - Task 4}

# set the coordinate limits for the chosen electorates
crop_map_MWR <- vicmap_sa1_G02_electorates_grouped_MWR %>% 
  st_crop(xmin = 144.8, xmax = 145.2,
          ymin = -38.1, ymax = -37.6)

cropped_map_MWR <- ggplot(crop_map_MWR) + 
  geom_sf(aes(geometry = geom, fill = Median_rent_weekly))

cropped_map_MWR

```

Importantly, a map consist of name of the locations, similarly we label the locations of the map as below

```{r labelling the Map MWR - Task 4}

data_for_labels = crop_map_MWR %>% 
      filter(DivisionNm %in% c("Kooyong", "Goldstein", "Melbourne", "Menzies","Maribyrnong", "Wills", "Scullin", "McEwen", "Chrisholm"))

cropped_map_MWR +
  geom_sf_label(data = data_for_labels,
    aes(label = DivisionNm, geometry = geom),
    size = 2)	

```
### Observations on Median weekly rent:

<u>Rent Differences Across Electorates:<u/>

In Goldstein County, the median rent is over AUD 550 per week.
Kooyong, with rents exceeding AUD 500 per week.
Meanwhile, in Menzies County, the median rent is nearly AUD 450 per week.


<u>Urban vs. Suburban Rent Trends:<u/>

  - We observe a trend where median rent decreases as we move from urban to suburban areas.
  - Suburbs like Scullin, Wills, and Marribyrnong have notably lower weekly rents compared to the urban areas, illustrating more affordable housing options in these areas.

<u>Median Total Personal Income Weekly:<u/>


```{r Map data MTPIW - Task 4}
aec_map <- read_sf(here::here("data/vic-july-2021-esri/E_VIC21_region.shp"))
```

```{r Wrangling data for Map M_tot_prsnl_inc_w - Task 4}

# Set projection to GDA1994 using EPSG:4283
st_crs(aec_map$geometry,4283)
  
# Transform projection from GDA1994 to GDA2020 using EPSG:7844
aec_map$geometry = st_transform(aec_map$geometry, 7844) 

# Get SA1 Centroids
vicmap_sa1_G02_w_centroid <- vicmap_sa1_G02 |>
  mutate(centroid = st_centroid(geom))

# Determine with SA1 centroids overlap with which electoral regions
electoral_intersects = st_intersects(vicmap_sa1_G02_w_centroid$centroid, 
                               aec_map$geometry, 
                               sparse = FALSE) 
arr_ind = which(electoral_intersects == TRUE, arr.ind = TRUE)
sa1_ind = arr_ind[,1] 
division_ind = arr_ind[,2]
division_name = aec_map$Elect_div[division_ind]
sa1_name = vicmap_sa1_G02_w_centroid$SA1_NAME_2021[sa1_ind]

# Save the SA1 region and its matching electorate into a data frame
sa1_divisions = data.frame(SA1_NAME_2021 = sa1_name, 
                           DivisionNm = division_name)

# Add the electorate names to the map
vicmap_sa1_G02_electorates  <- vicmap_sa1_G02 %>% 
  right_join(sa1_divisions)

# Combine the data from electorates together using group_by
vicmap_sa1_G02_electorates_grouped_MTPIW = vicmap_sa1_G02_electorates |>
  group_by(DivisionNm) |> 
  summarise(Median_tot_prsnl_inc_weekly = mean(Median_tot_prsnl_inc_weekly)) |>
  ungroup()

# Plot results to check assignment

VIC_map_MTPIW <- ggplot() +
   geom_sf(data = vicmap_sa1_G02_electorates_grouped_MTPIW,
           aes(geometry = geom, fill = Median_tot_prsnl_inc_weekly)) + 
  theme_bw() +
  theme(legend.position = "bottom")
VIC_map_MTPIW

```

```{r Scoped view of Map MTPIW - Task 4}

# set the coordinate limits for the chosen electorates
crop_map_MTPIW <- vicmap_sa1_G02_electorates_grouped_MTPIW %>% 
  st_crop(xmin = 144.8, xmax = 145.2,
          ymin = -38.1, ymax = -37.6)

cropped_map_MTPIW <- ggplot(crop_map_MTPIW) + 
  geom_sf(aes(geometry = geom, fill = Median_tot_prsnl_inc_weekly))

cropped_map_MTPIW

```

```{r labelling the Map MTPIW - Task 4}

data_for_labels = crop_map_MTPIW %>% 
      filter(DivisionNm %in% c("Kooyong", "Goldstein", "Melbourne", "Menzies","Maribyrnong", "Wills", "Scullin", "McEwen", "Chrisholm", "Fraser", "Higgins", "Hotham"))

cropped_map_MTPIW +
  geom_sf_label(data = data_for_labels,
    aes(label = DivisionNm, geometry = geom),
    size = 2)	

```